Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2015-01-20 paper/poly.tex
add a lemma about multiplication of binomial coeffs

@@

@@

>>>>

\documentclass[nocopyrightspace,preprint,pldi]{sigplanconf-pldi15}

\usepackage[utf8]{inputenc} %for utf8 input
\usepackage{amssymb} %for shift symbol
\usepackage{amsmath}
\usepackage{listings} %for code
\usepackage{mathpartir} %for typing rules
\usepackage{microtype} %better micro typing
\usepackage{stmaryrd} %for llbracket
\usepackage{mathabx} % for boxes
\usepackage{graphicx} %to include png images
\usepackage{xcolor} %for colors
\usepackage{url}
\usepackage{enumitem}
\usepackage{array} %for stupid tables

%----------------------------------------------------

\usepackage{prettyref}
\newcommand{\pref}[1]{\prettyref{#1}}
\newcommand{\Pref}[1]{\prettyref{#1} \vpageref[]{#1}}
\newcommand{\ppref}[1]{\vpageref[]{#1}}
\newrefformat{fig}{Figure~\ref{#1}}
\newrefformat{app}{Appendix~\ref{#1}}
\newrefformat{tab}{Table~\ref{#1}}
\newrefformat{cha}{Challenge~\ref{#1}}
\newrefformat{compiler}{Point~\ref{#1} of \pref{thm:compiler}}

%----------------------------------------------------

\usepackage{amsthm}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

%----------------------------------------------------

\input{definitions}
\begin{document}

@@

\subsection{Binomial basis}

\begin{lemma}
  There exists a family $(c^{ij}_k)_k$, such that
  $$
  \sum_k c^{ij}_k \binom n k = \binom n i \binom n j,
  $$
  and $c^{ij}_k = \binom k j \binom j {i+j - k}$ satisfies
  the previous equation.
\end{lemma}
\begin{proof}
  \begin{align*}
    \binom n i \binom n j
      &= \sum_k \binom {n-j} k \binom j {i-k} \binom n j \\
      &= \sum_k \binom {n-j} {k-j} \binom n j \binom j {i+j-k} \\
      &= \sum_k \binom n k \binom k j \binom j {i+j-k}.
  \end{align*}
  In the first equality, we use Vandermonde's convolution
  formula on $\binom n i$.  In the second equality we change
  the summation variable to $k-j$.  And in the third equation
  we use the identity proved below.
  \begin{align*}
    \binom {n-j} {k-j} \binom n j
      &= \frac {(n-j)!} {(n-k)! (k-j)!} \; \frac {n!} {(n-j)! j!} \\
      &= \frac {n!} {(n-k)! (k-j)! j!} \\
      &= \frac {n!} {(n-k)! k!} \; \frac {k!} {(k-j)! j!} \\
      &= \binom n k \binom k j.
  \end{align*}
\end{proof}

@@

\end{document}
